Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-02-01 Documents/Talk/content.tex
Exoplanet figure

\begin{frame}[t]{View of data analysis}
All conclusions are probabilities.

The only difference between data analysis methods is what prior information
they assume.
\end{frame}

@@

\begin{frame}[t]{Nested Sampling}
In 2004, John Skilling introduced {\bf Nested Sampling}, a technique
that starts with the prior distribution, and shrinks volume at a controlled
rate. Maps big space into easy 1-D problem.

Resolves phase transition problem, and helps a little with multiple modes \&
strong degeneracies. Figure from Skilling (2006).

\begin{figure}
\begin{center}
\includegraphics[scale=0.2]{ns.png}
\end{center}
\end{figure}

@@

>>>>

\begin{frame}[t]{View of data analysis}
All conclusions are probabilities.
\vspace{20pt}

The only difference between data analysis methods is what prior information
they assume, and what numerical methods are used to calculate the result.
\end{frame}

@@

\begin{frame}[t]{Nested Sampling}
In 2004, John Skilling introduced {\bf Nested Sampling}, a technique
that starts with the prior distribution, and shrinks volume at a controlled
rate.
\vspace{20pt}

{\bf Nested Sampling solves the problem of phase transitions}.
\end{frame}

@@

\begin{frame}[t]{Exoplanets}
Radial velocity data is considered challenging
\end{frame}

\begin{frame}[t]{Exoplanets: Simulated Dataset}
How many planets?
\begin{center}
\includegraphics[scale=0.35]{ExoplanetFigures/fake_data.pdf}
\end{center}
\end{frame}
